\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontspec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    citecolor=blue,
    pdfborder={0 0 0},
    linkbordercolor=blue,
    urlbordercolor=cyan
}

\setmainfont{Liberation Sans}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}

\begin{document}

\begin{center}
    \textbf{\Huge Jordon Leach} \\
    \vspace{2mm}
    \textbf{Senior Software Engineer} \\
    \vspace{2mm}
    Glen Rock, Pennsylvania, United States \\
    (717) 781-7700 \\
    \href{mailto:jordonleach@gmail.com}{jordonleach@gmail.com} \\
    \href{https://jordonleach.dev}{\underline{Personal Website}} \textbar\ 
    \href{https://github.com/jordojordo}{\underline{GitHub}}
\end{center}

\vspace{5mm}

\section*{Profile}
Innovative Senior Software Engineer with a proven track record of delivering modern, large-scale frontend and backend solutions. Comprehensive experience with \textbf{Vue.js}, \textbf{React}, \textbf{Node.js}, and \textbf{Kubernetes}, underpinned by strong DevOps practices and leadership. Skilled in cross-functional collaboration, architectural design, and optimizing deployment pipelines. Passionate about open-source contributions and driving impactful user experiences.

\section*{Core Skills}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Frontend:} JavaScript (ES6+), TypeScript, Vue.js, React, Modern CSS (SCSS, responsive design)
    \item \textbf{Backend:} Node.js, Express, RESTful APIs, WebSockets, Postgres, MySQL
    \item \textbf{DevOps:} Kubernetes, Rancher, Helm, Docker, NGINX, CI/CD pipelines, GitHub Actions
    \item \textbf{Cloud and Deployment:} Distributed systems, container orchestration, cluster management
    \item \textbf{Embedded Systems:} C++, ESP32 programming, real-time communication protocols
    \item \textbf{Other:} Leadership, mentoring, technical documentation, agile workflows, cross-functional collaboration
\end{itemize}

\section*{Employment History}

\subsection*{Senior Software Engineer, SUSE}
\textit{Remote} \hfill \textbf{Aug 2021 — Present}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Promotion and Leadership:} Promoted to Senior Software Engineer for leading cross-team initiatives and delivering critical UI features.
    \item \textbf{Kubewarden UI:} Main creator of the \textit{Kubewarden UI} (143,000+ lines of code), leveraging TypeScript + Vue.js to improve user experience and scalability for Kubernetes policy management.
    \item \textbf{Rancher Dashboard:} Contributed to end-to-end testing and UI enhancements, raising system reliability and user satisfaction for thousands of users globally.
    \item \textbf{Helm Chart Innovations:} Authored Helm charts for Rancher Extensions, reducing deployment complexity and boosting adoption of new features.
    \item \textbf{Testing \& Documentation:} Wrote comprehensive unit and end-to-end tests (48\% coverage), strengthening code stability and project visibility.
    \item \textbf{Community Engagement:} Presented at SUSECON (2,000+ attendees) and led technical webinars (3,000+ accumulated views), fostering community involvement.
    \item \textbf{Rancher Extensions:} Developed the \texttt{@shell/rancher} package powering 200+ Rancher Manager extensions, supporting CI/CD integrations, air-gapped builds, and enterprise deployments.
\end{itemize}

\subsection*{Webmaster, Cadmium}
\textit{Forest Hill, Maryland} \hfill \textbf{Oct 2019 — Jul 2021}
\begin{itemize}[leftmargin=1.5em]
    \item Unified four disparate company sites into a single cohesive platform using custom APIs and CI/CD pipelines.
    \item Collaborated with marketing and design teams to implement conversion-focused UI components and optimize site performance.
    \item Maintained reliability and functionality through automated tests and robust deployment strategies.
\end{itemize}

\subsection*{Web Developer, Freelance}
\textit{Remote} \hfill \textbf{Jun 2018 — Oct 2019}
\begin{itemize}[leftmargin=1.5em]
    \item Built and maintained WordPress and React.js e-commerce sites with intuitive UIs and integrated payment solutions (Stripe).
    \item Improved website performance and SEO rankings through analytics-driven optimization.
    \item Implemented responsive web design principles and modern CSS to enhance the user experience.
\end{itemize}

\section*{Select Projects \& Achievements}

\subsection*{Horus Holdings (React, MySQL, Docker)}
\textit{Cash flow management tool for real-time financial insights}
\begin{itemize}[leftmargin=1.5em]
    \item Created a full-stack application using \textbf{React} (frontend) and Node.js (backend) with \textbf{MySQL} for secure user authentication and data persistence.
    \item Built Dockerized microservices enabling quickstart scripts for seamless local and production deployments.
    \item Incorporated \textbf{CI/CD pipelines} and container orchestration best practices to streamline updates and ensure high availability.
\end{itemize}

\subsection*{ThothScript \& ThothScript Operator (Vue.js, Node.js, Kubernetes)}
\textit{Chatbot + Operator for automated Kubernetes management via natural language scripting}
\begin{itemize}[leftmargin=1.5em]
    \item Developed a \textbf{Vue.js}-based chatbot UI that interfaces with a Node.js operator, harnessing GPTScript to provision Kubernetes resources.
    \item Leveraged \textbf{Helm} for deployment, enabling flexible \textbf{Kubernetes} configurations and scaling across clusters.
    \item Architected WebSocket communication for real-time feedback, bridging user-friendly NLP with low-level Kubernetes commands.
\end{itemize}

\subsection*{Endernet UWB (Vue.js, Node.js, Postgres, ESP32, C++)}
\textit{UWB trilateration system with automation for anchor distance calculations}
\begin{itemize}[leftmargin=1.5em]
    \item Developed modular firmware in \textbf{C++} for \textbf{ESP32} microcontrollers, enabling real-time communication with \textbf{DWM1000} modules via \textbf{UDP} and \textbf{WebSockets}.
    \item Engineered a scalable backend using \textbf{Node.js} and \textbf{Postgres} for anchor distance calculations, user management, and configuration storage.
    \item Designed a \textbf{Vue.js} frontend for visualizing real-time UWB anchor and tag data, including automated distance calibration routines.
\end{itemize}

\subsection*{Other Personal Projects}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Lawndon}: Eco-friendly, remote-controlled electric lawn mower with automated builds using GitHub Actions.
    \item \textbf{Yokanga}: A retro-themed music video streaming website, utilizing cloud-native technologies for hosting and streaming.
    \item \textbf{Daphine Streaming API}: Containerized media streaming API deployed on Kubernetes via Rancher.
    \item \textbf{Hermes (3D Web App)}: Built with Vue.js + Three.js, deployed on a homelab cluster demonstrating advanced UI/UX and 3D rendering.
\end{itemize}

\section*{Additional Experience}

\subsection*{Photo Lab Technician, Techlab Photo}
\textit{Baltimore, Maryland} \hfill \textbf{Oct 2017 — Jun 2018}
\begin{itemize}[leftmargin=1.5em]
    \item Automated data management with a custom internal database, improving operational workflows.
    \item Troubleshot and maintained specialized photo processing equipment under tight deadlines.
\end{itemize}

\subsection*{Aircraft Armament Systems Journeyman, US Air Force}
\textit{Multiple locations} \hfill \textbf{Aug 2010 — Nov 2014}
\begin{itemize}[leftmargin=1.5em]
    \item Maintained F-16 aircraft weapon systems in high-stakes environments, ensuring uptime and reliability.
    \item Conducted malfunction analyses and collaborated on cross-functional teams with precision and discipline.
\end{itemize}

\end{document}
